### 2024-05-31 Manuscript/main.tex
Abstract 1st draft

\section{Abstract}
Objective: Showing which patterns are recovered by different functional diversity metrics under different frameworks and how different metrics recover different signals from different processes linked to common mechanisms in ecology.

Approach: We simulate some one dimensional datasets using neutral evolutionary models (pure birth tree with brownian motion traits) then perturb the resulting dataset with some common ecological stressor mechanisms (environmental filtering, competitive exclusion, equalising fitness and facilitation).
We then measure different space occupancy metrics on the perturbed and unperturbed simulations and check how the different metrics capture the resultant changes.

>>>>

\section{Abstract}

Functional diversity is now a commonly used statistic to describe populations and communities in ecology beyond specific richness.
It is a very efficient tool allowing to summarise a complex space occupancy pattern (what is changing?) that can be used to understand changes in communities and/or populations (the process; how is it changing?) in response to some stressors (the mechanism; why is it changing?). 
However, although researchers have the choice between many different metrics (what) to study their questions of interest (how and why), it is often not directly clear which metric is more readily appropriate for which question.
Here we show which patterns are recovered by different functional diversity metrics under different frameworks and how different metrics recover different signals from different processes linked to common mechanisms in ecology.
Using both simulated data with different common ecological mechanisms approximations (environmental filtering, competitive exclusion, equalising fitness and facilitation) and an empirical dataset affected by more complex and nuanced mechanisms; we test the effectiveness of different space occupancy metrics to recover the simulated or empirical changes.
We show that different metrics perform better for different tasks and discuss the importance of not using a one-fit-all metric but rather think and test whether a particular one will be good at capturing a pattern of interest.
